Estimation of the perceived time of presence of sources in urban acoustic environments using deep learning techniques

### 2019-06-18 paper/paperV1.tex
Added links

Discrepancies between projections of original and replicated scenes are highlighted in Figure~\ref{fig:pspace_rec} using arrows. The standard deviation of assessments is represented using ellipses for one location (P1). The projections of assessment distributions consistently overlap for all pairs of recorded and replicated scenes\footnote{Data available here \url{http://felixgontier.github.io/soundSourcePresenceEstimation/index.html}}. This illustrates the results in Table~\ref{tab:ogrep} where perceptual assessments were not found to differ significantly overall.

>>>>

Discrepancies between projections of original and replicated scenes are highlighted in Figure~\ref{fig:pspace_rec} using arrows. The standard deviation of assessments is represented using ellipses for one location (P1). The projections of assessment distributions consistently overlap for all pairs of recorded and replicated scenes\footnote{Data available here \url{http://felixgontier.github.io/soundSourcePresenceEstimation/web/index.html}}. This illustrates the results in Table~\ref{tab:ogrep} where perceptual assessments were not found to differ significantly overall.
